The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-08-29 design.tex
main content finished
start to draw diagram

Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.
% \begin{table}[htbp]
%   \centering
%   \scriptsize
%   \caption{Simple resource configuration}
%     \begin{tabular}{ccc}
%     \toprule
%     Resource & Type  & Capacity \\
%     \midrule
%     $r_1$ & 1     & 10 \\
%     $r_2$ & 2     & 10 \\
%     $r_3$ & 3     & 10 \\
%     $r_4$ & 3     & 10 \\
%     \bottomrule
%     \end{tabular}%
%   \label{tab:simpleresourceconfiguration}%
% \end{table}%
\begin{table}[htbp]
  \centering
  \scriptsize
  \caption{Simple job configuration}
    \begin{tabular}{cccccc}
    \toprule
    \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
    \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
    \midrule
    $t_1$ & 0     & 5     & 7     & 0     & 7 \\
    $t_2$ & 7     & 5     & 7     & 4     & 5 \\
    $t_3$ & 6     & 0     & 5     & 2     & 3 \\
    $t_4$ & 9	 & 4  & 6 & 1 &2 \\
    $t_5$ & 1 & 0 & 3 & 2 & 3\\
    $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
    $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
    \bottomrule
    \end{tabular}%
  \label{tab:simplejobconfiguration}%
\end{table}%
\begin{figure}[htbp]
	\centering
	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
	\caption{Simple instance schedule chart with 4 resources}
	\label{fig:scheduleChart}
\end{figure}
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period. Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.

@@

\begin{table}[htbp]
  \scriptsize
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\large\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ , $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Product quality produced via service $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource type\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

>>>>

% Specifically, a simple instance with configuration \autoref{tab:simplejobconfiguration} and schedule chart \autoref{fig:scheduleChart} will describe the setting more clearly.

% \begin{table}[htbp]
%   \centering
%   \scriptsize
%   \caption{Simple job configuration}
%     \begin{tabular}{cccccc}
%     \toprule
%     \multicolumn{1}{c}{\multirow{2}[0]{*}{ Job}} & \multicolumn{3}{c}{Need Resource Capacity} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Release Time}} & \multicolumn{1}{c}{\multirow{2}[0]{*}{Process Duration}} \\
%     \multicolumn{1}{c}{} & $Type_1$ & $Type_2$ & $Type_3$ & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
%     \midrule
%     $t_1$ & 0     & 5     & 7     & 0     & 7 \\
%     $t_2$ & 7     & 5     & 7     & 4     & 5 \\
%     $t_3$ & 6     & 0     & 5     & 2     & 3 \\
%     $t_4$ & 9	 & 4  & 6 & 1 &2 \\
%     $t_5$ & 1 & 0 & 3 & 2 & 3\\
%     $sc_1$ & 0     & 0     & 3    & 1     & 1 \\
%     $sc_2$ & 2     & 7     & 6     & 3     & 1 \\
%     \bottomrule
%     \end{tabular}%
%   \label{tab:simplejobconfiguration}%
% \end{table}%
% \begin{figure}[htbp]
% 	\centering
% 	\resizebox{.8\textwidth}{!}{\input{figures/scheduleChart}}
% 	\caption{Simple instance schedule chart with 4 resources}
% 	\label{fig:scheduleChart}
% \end{figure}
This instance makes some simplification in the subscript fields in order to emphasize the resource cooperation, all the job(task and service-call) performance can only be started when the each of the related resource is ready, so the shadow in the figure is the waiting period. Horizontal dotted line constrained the available capacity of the resource for the following jobs, every performance of service-call will make the line lower and it will never get higher again unless the related service is repealed.

@@

\begin{table}[htbp]
  \scriptsize
\begin{tabularx}{\textwidth}{|lX|}
    \hline
    \multicolumn{2}{|l|}{\multirow{2}[0]{*}{\textbf{Nomencalture}}} \\
    \multicolumn{2}{|l|}{} \\
	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\
	$p_{ij}$ & Process duration of $t_{ij}$\\
	$\gamma_{ij}$ & Expect quality of product after the finish of $t_{ij}$\\
	$r_i$ & Release time of $o_i$\\
	$f_{ij}$ & Actual finish time of $t_{ij}$ \\
	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\
	$C_{k,\tau}$ & Capacity of $mr_k$ at time $\tau$\\
	$A_{k,\tau}$ & Available capacity of $mr_k$ at time $\tau$\\
	$\mathcal{L}_{k,\tau}$ & The list of job queue of $mr_k$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $mr_k$ at $\tau$ \\ 
	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\
	$sc_l$ & Service-call generated by provider\\
	$p_l$ & Process duration of $sc_l$\\
	$r_l$ & Release time of $sc_l$\\
	$\mathcal{P}_{l}$ & The set of predecessor of $sc_{l}$\\
	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ , $\mathcal{A}_l\subset\mathcal{A}$\\
	$ms_l$ & Service that generated after the finish of $sc_l$\\
	$\Delta_l$ & Product quality produced via service $ms_l$\\
	$\bm{mr}_l$ & Resource member set of $ms_l$\\
	$\bm{q}_l$ & Resource member's capacity contribution set of $ms_l$\\
	$\mathcal{L}_{l,\tau}$ & The list of job queue of $ms_l$ at $\tau$ with sequence\\
	$\mathcal{G}_{k,\tau}$ & The set of active job (being processed) of $ms_l$ at $\tau$ \\
	$\mathcal{R}_{ij,\tau}$ & Resource candidates set for $t_{ij}$ to select\\
	$\mathcal{B}_{ij,\tau}$ & Resource candidate types set for $t_{ij}$\\
	$\mathcal{S}_{ij,\tau}$ & Service candidates set for $t_{ij}$ to select\\
	$\mathcal{R}_{l,\tau}$ & Resource candidates set for $sc_l$ to select\\
	$\mathcal{B}_{l,\tau}$ & Resource candidate types set for $sc_l$\\
	$R(\cdot)$ & Rank inquire function about provider\\
	$F(\cdot)$ & Owner inquire function about resource or service\\
	$P(\cdot)$ & Type inquire function about resource type\\
	$\bm{x}$ & Bold font of the variable($x$) means the temp set of a bunch of these variables\\
    \hline
\end{tabularx}
\end{table}

### 2016-08-29 result.tex
start to draw diagram

    \bottomrule
    \end{tabular}
\end{table}
we find: \begin{inparaenum}[1)]
\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22, this combined mode even also need lower number of queue length. Full lines are not much above dotted lines in $N_F$ means that task processing velocity will be a little slower with the metabolism, exception also appears in Mode 22. 
\item $L$ and $N_T$ both represent the waiting of job, triangle and square line turned lower in $L$ meas that service-incubate mode can help reduce the waiting of job, these two type of line appeared above the circle line means the service-incubate mode do accelerate the processing velocity.
\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsource mode needs more resources to operate and can only reduce the waiting of job a little.
\item There is no big difference among all the 6 modes. Provider in metabolism mode will get lower rank value for they cannot stay in the system forever, the longer stay in the system, the higher rank value provider will get. Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast without service-incubate mode.
\item Mode 22 is a very special mode that reached the balance of the system, although all the mentioned modes will reach balance in the long run, with the average data value shown in \autoref{tab:averagevalue}, metabolism with service-incubate but not with outsource mode is the easiest combine mode to maintain the system, resource are self configured and controlled to just meet the task need.
\end{inparaenum}

>>>>

    \bottomrule
    \end{tabular}
\end{table}
we find: \begin{inparaenum}[1)]
\item Most dotted lines are above the full lines with the same series in $N_R,N_P,N_T$ means that metabolism mode need lower number of provider and resource, with the price of higher number of queue length of the tasks in resources in the system to deal with the same amount of needs, except for Mode 22, this combined mode even also need lower number of queue length. Full lines are not much above dotted lines in $N_F$ means that task processing velocity will be a little slower with the metabolism, exception also appears in Mode 22. 
\item $L$ and $N_T$ both represent the waiting of job, triangle and square line turned lower in $L$ meas that service-incubate mode can help reduce the waiting of job, these two type of line appeared above the circle line means the service-incubate mode do accelerate the processing velocity.
\item Triangle lines are a little above the square lines in $N_R,N_P,N_T$ means that outsource mode needs more resources to operate and can only reduce the waiting of job a little.
\item There is no big difference among all the 6 modes. Provider in metabolism mode will get lower rank value for they cannot stay in the system forever, the longer stay in the system, the higher rank value provider will get. Provider in Mode 11 even will not promote their rank value, which means that the metabolism rate is very fast without service-incubate mode.
\item Mode 22 is a very special mode that reached the balance of the system that the number of provider and resource changed little with time goes by and it means all the ..., theoretically all the metabolism related modes will reach balance in the long run because the coming order velocity less than the resources, but the appearance of service-call and metabolism itself is full of uncertainty and it's hard to predict when other metabolism related mode will get the balance. , with the average data value shown in \autoref{tab:averagevalue}, metabolism with service-incubate but not with outsource mode is the easiest combine mode to maintain the system, resource are self configured and controlled to just meet the task need.
\end{inparaenum}

### 2016-08-29 review.tex
start to draw diagram

Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (Tao, Zhang, et al. 2012;Valilai and Houshmand 2013)

Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions. For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on

>>>>

Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (\cite{Tao2012}\cite{Valilai2013}
